\centerline{Sudoku}

### 2021-05-25 report/paper.tex

\abstract {
The aim of this project is to make an Encoder and Decoder for a SAT-solver in order to decide whether a problem is satisfiable or unsatisfiable. WRITE A BETTER ABSTRACT
}

>>>>

\abstract {
Sudoku is a Swiss game often confused as japanese because of its japanese
sounding name.

Sudokus are puzzles composed by numbers that are structured in a $9 \times 9$ table.
At the beginning of the game the Sudoku board only a few cells contain numbers,
which are ``randomly'' positioned in
the table.

The main purpose of the game is to fill the table without repeating numbers
in a ``box'' or in the entire row or column of the table.

The aim of this
project is to make an Encoder and Decoder for a SAT-solver in order to decide
whether a given input board is solvable or not, and when solvable to find a
feasible solution.

A Sudoku is valid when all of its rows are valid
(each row must not have repeating numbers), when all of its columns
are valid (each column must not have repeating numbers),
and when all of the $3 \times 3$ boxes in the board are valid
(each box must not have repeating numbers).

To develop the code of the project
we used Python3, specifically using the pip3 package z3-solver (official
library to write logics for SAT solver).
}
